Low Infant Birth Weight in Brazil

### 2024-02-23 products/manuscript/Manuscript_Cassia.qmd
Part 2
Fixed tables with Savannah Hammerton's help

There were three continuous variables: maternal age, infant birth weight, and infant length. I am aware that this table is not rendering correctly in the word document, but I am unable to figure out why. If I load library(gt), then my word document is corrupted and will not open at all. I will continue to work on this issue. 
```{r}
#| label: tbl-summarytablecont
#| tbl-cap: "Continous Data Summary Table"
#| echo: FALSE
summary_stats_table <- readRDS(here::here("results", "tables", "summary_stats_table.rds"))
summary_stats_table
```

>>>>

There were three continuous variables: maternal age, infant birth weight, and infant length. I am aware that this table is not rendering correctly in the word document, but I am unable to figure out why. If I load library(gt), then my word document is corrupted and will not open at all. I will continue to work on this issue. 
```{r}
#| label: tbl-summarytablecont
#| tbl-cap: "Continous Data Summary Table"
#| echo: FALSE
summary_stats_table <- readRDS(here::here("results", "tables", "summary_stats_table.rds"))
summary_stats_table |> gt::as_raw_html()
```
